%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article} 
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
		\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
		\item\small{ \textbf{#1}{: #2 \vspace{-2pt}}}
}
\newcommand{\resumeSingleItem}[1]{
		\item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheadingDouble}[2]{
		\vspace{-1pt}\item
				\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2
				\end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingSingle}[1]{
		\vspace{-1pt}\item {
				\textbf{#1}
		}
}

\newcommand{\resumeSubheading}[4]{
		\vspace{-1pt}\item
				\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
				\textit{\small#3} & \textit{\small #4} \\
				\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{center}
	\textbf{\href{http://www.muhammadtello.com/}{\LARGE Muhammad Tello}}  \\
	\setlength{\tabcolsep}{5pt}
	\begin{tabular}{l | c | r}
	+1-734-709-8401 & \href{mailto:mitello@wccnet.edu}{mitello@wccnet.edu} & 
		\href{https://github.com/ijaazt}{https://github.com/ijaazt}
	\end{tabular}
\end{center}



%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
	\resumeSubheading
	{Washtenaw Community College}{Ann Arbor, MI}
	{Associate in Science Computer Science: Programming in Java}{December 2019}
\resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
	\resumeItem{Languages}{Java, Kotlin, JavaScript, Python, C}
	\resumeItem{Technologies}{React, Spring, Git}
	\resumeItem{Technical Management}{Project Management, Troubleshooting, Installation}
	\resumeItem{Operating Systems}{Android, Linux/Unix, Windows XP - 10}
\resumeSubHeadingListEnd

%-----------Academic PROJECTS-----------------
\section{Experience}
\resumeSubHeadingListStart

	\resumeSubheadingDouble{Blog}{Web}
	\resumeItemListStart
		\resumeSingleItem
		{Used Spring to create a backend rest api that includes all CRUD operations}
		\resumeSingleItem
		{Used ReactJS to create a front-end blog}
	\resumeItemListEnd


	\resumeSubheadingDouble{Postboard}{Web}
	\resumeItemListStart
		\resumeSingleItem
		{Developed a simple multi-user post application.}
		\resumeSingleItem
		{Used JDBC to create and manipulate a MySQL Database of user info and post content.}
		\resumeSingleItem
		{Used Servlets to create a REST API.}
		\resumeSingleItem
		{Used JavaScript and Bootstrap to create a user interface.}
	\resumeItemListEnd

	\resumeSubheadingDouble
	{Movie Lists}{Android}
	\resumeItemListStart
		\resumeSingleItem
		{Used MVC, APIs, View Models to save movies into a database viewable by the user}
		\resumeSingleItem
		{Architectured application to use fragments to showcase compartmentalized UI}
		\resumeSingleItem
		{Implemented a Recycler adapter to convert movie data to be viewable on the screen}
		\resumeSingleItem
		{Designed fully asynchronous application using threads, callables and live data}
	\resumeItemListEnd

	\resumeSubheadingDouble{Pong Game}{Desktop}
	\resumeItemListStart
		\resumeSingleItem
		{Co-created a multiplayer cross-platform pong game that paid homage to the Atari game using AWT}
		\resumeSingleItem
		{Given a fully developed framework created an networked MVC game}
	\resumeItemListEnd

	\resumeSubheading
	{Washtenaw Community College}{Ann Arbor, MI}
	{Lab Aide}{December 2017 - Present}
	\resumeItemListStart
		\resumeItem{Student Worker, Computer Classroom Lab Aide}{}
		\resumeItemListStart
			\resumeSingleItem
			{Provides direct support to students and faculty during CIS classes.}
			\resumeSingleItem
			{Proactively assist students with technology use during class sessions.}
			\resumeSingleItem
			{Clean classrooms during school breaks.}
			\resumeSingleItem
			{Support external groups, such as UA and Ironworkers.}
			\resumeSingleItem
			{Support group study sessions.}
		\resumeItemListEnd

		\resumeItem{Group Study Facilitator/Support}{}
		\resumeItemListStart
			\resumeSingleItem
			{Provides direct support to students during Group Study sessions.}
			\resumeSingleItem
			{Assist students with assignments for courses within discipline.}
			\resumeSingleItem
			{Assist in the installation of O.S. on student computers including installation of updates, drivers, additional apps, and activation which must be tracked by student.}
			\resumeSingleItem
			{Proactively assist students with computer software during group study sessions.}
		\resumeItemListEnd
	\resumeItemListEnd
	\resumeSubheading
	{Starbucks}{Ann Arbor, MI}
	{Barista}{November 2016 - Present}

\resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
